Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-31 paper-for_arxiv/paper.tex
Taking care of proper Journal formatting
fixing elderly people
working on influence stuff, lots of notes but not finished
fixing margins and title

%%File: formatting-instruction.tex
\documentclass[]{article}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
%\usepackage{amssymb, amsmath, amsthm}
%\usepackage{graphicx}
%\usepackage{multirow}
%\usepackage{bigstrut}
%\usepackage{booktabs}
%\usepackage{multirow,bigstrut}
%\usepackage{tabu}
\usepackage{authblk}
%\usepackage{color}
%\usepackage{subfigure}
%\usepackage{appendix}
%%\frenchspacing
%%\setlength{\pdfpagewidth}{8.5in}
%%\setlength{\pdfpageheight}{11in}
%\textwidth=126mm

@@

@@

\title{Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection}

@@

%\shorttitle{Followers Are Not Enough}
%\shortauthorlist{D. Darmon \emph{ET AL.}} %%% for verso running head

@@

\begin{abstract}
%\begin{quote}
%The Keywords
%Community detection, functional communities, social network analysis

@@

%\bibliographystyle{comnet}
\bibliographystyle{plainnat}
\bibliography{references.bib}

>>>>

%%File: formatting-instruction.tex
\documentclass{article}
\usepackage{authblk}
%\usepackage{color}
%\usepackage{subfigure}
%\usepackage{appendix}
%%\frenchspacing
%%\setlength{\pdfpagewidth}{8.5in}
%%\setlength{\pdfpageheight}{11in}
%\textwidth=126mm

@@

\newcommand{\alert}[1]{{\color{red}#1}}

% *** Do not adjust lengths that control margins, column widths, etc. ***
%\oddsidemargin= 0.25in % 1in margins at left and right
%\evensidemargin= 0in
\textwidth= 5in % US paper is 8.5in wide     ultra conservative = 5in
\marginparwidth= 0in

\textheight=7.6667in % US paper is 11.0in high %%% ultra conservative = 7.6in

@@

\title{Followers Are Not Enough: A Question-Oriented Approach to Community Detection}

@@

%BELOW IS FOR JCN guidelines
%\shorttitle{Followers Are Not Enough}
%\shortauthorlist{D. Darmon \emph{ET AL.}} %%% for verso running head

@@

\begin{abstract}
%\begin{quote}
%The Keywords
%Community detection, functional communities, social network analysis, transfer entropy

@@

\bibliographystyle{comnet}
%\bibliographystyle{plainnat}
\bibliography{references.bib}
